### 2009-10-20 doc/manuals/chelonia/arc-storage-manual.tex
Chelonia administrator's manual is more or less updated (using INI configs, and the latest trunk).

This section shows how to install Chelonia on a freshly installed debian lenny machine.

Get the latest ARC code from the subversion (\verb!http://svn.nordugrid.org/!):

\begin{verbatim}
$ svn co http://svn.nordugrid.org/repos/nordugrid/arc1/trunk arc1
\end{verbatim}

Check the README file for all the dependencies, and install them. Here `aptitude' is used, but of course on other Linux distribution different package management software may be used, and the name of the packages may differ as well.

\begin{verbatim}
$ sudo aptitude install build-essential
$ sudo aptitude install autoconf
$ sudo aptitude install gettext
$ sudo aptitude install cvs
$ sudo aptitude install libtool
$ sudo aptitude install pkg-config
$ sudo aptitude install libglibmm-2.4-dev
$ sudo aptitude install python-dev
$ sudo aptitude install swig
$ sudo aptitude install libxml2-dev
$ sudo aptitude install libssl-dev
\end{verbatim}

Now, run the \verb!autogen! and \verb!configure! scripts (target directories for the installation may be specified with the \verb!--prefix! option):

\begin{verbatim}
$ cd arc1
$ ./autogen.sh
$ ./configure --disable-java --disable-a-rex-service --disable-isi-service \
    --disable-charon-service --disable-compiler-service \
    --disable-paul-service --disable-sched-service

Unit testing:       yes
Java binding:       no
Python binding:     yes (2.5)

Available third-party features:

RLS:                no
GridFTP:            no
LFC:                no
RSL:                no
SAML:               no
MYSQL CLIENT LIB:   no
gSOAP:              no

Included components:
A-Rex service:      no
ISI service:        no
CHARON service:     no
HOPI service:       yes
SCHED service:      no
STORAGE service:    yes
PAUL service:       no
SRM client (DMC):   no
GSI channel (MCC):  no

Start with compiling it:

\begin{verbatim}
$ make
\end{verbatim}

And then install it (you need to be root if you want to install it to the default location):

\begin{verbatim}
$ sudo make install
\end{verbatim}

It may be a good idea to run \verb!ldconfig! to refresh the list of libraries:

\begin{verbatim}
$ ldconfig
\end{verbatim}

Check if the python packages are installed correctly:

@@

If there is no error on importing any of the packages, everything is OK. If the packages cannot be imported, try to set the PYTHONPATH environment variable to point to location of the packages.

It is important to syncronize the time of the machine - the storage system will make decisions based on differences between timestamps. When deploying multiple machines, different times will cause problems.

Host (and user) certificates are required to run the system. For testing purposes the NorduGrid InstantCA solution can be used. The InstantCA is capable of creating a demo-CA with short lifetime. The URL of the InstantCA service is \verb!https://vls.grid.upjs.sk/CA/instantCA!. Now, create 3 user and 3 host certificates. (for this example, set the Organization Name to `knowarc', the Common name of the CA to `storage-test', the name of the users to `penny', `billy' and `hammer' and the name of the hosts to `upsilon', `omicron' and `theta'. A password for the CA and passwords for the user certificates are needed as well, these should be at least 4 characters long).

@@

\begin{verbatim}
$ ls -lR
.:
total 28
drwxr-xr-x 2 zsombor zsombor 4096 2009-03-19 12:11 CA
-rw-r--r-- 1 zsombor zsombor  963 2009-03-19 12:11 ca.key
-rw-r--r-- 1 zsombor zsombor  786 2009-03-19 12:11 ca.pem
drwxr-xr-x 2 zsombor zsombor 4096 2009-03-19 12:11 hostCerts
-rw-r--r-- 1 zsombor zsombor 1044 2009-03-19 12:11 readme
-rw-r--r-- 1 zsombor zsombor    3 2009-03-19 12:11 serial.srl
drwxr-xr-x 2 zsombor zsombor 4096 2009-03-19 12:11 userCerts

./CA:
total 8
-rw-r--r-- 1 zsombor zsombor 786 2009-03-19 12:11 66fe707c.0
-rw-r--r-- 1 zsombor zsombor 139 2009-03-19 12:11 66fe707c.signing_policy

./hostCerts:
total 24
-rw-r--r-- 1 zsombor zsombor 786 2009-03-19 12:11 hostcert-omicron.pem
-rw-r--r-- 1 zsombor zsombor 782 2009-03-19 12:11 hostcert-theta.pem
-rw-r--r-- 1 zsombor zsombor 786 2009-03-19 12:11 hostcert-upsilon.pem
-rw-r--r-- 1 zsombor zsombor 887 2009-03-19 12:11 hostkey-omicron.pem
-rw-r--r-- 1 zsombor zsombor 891 2009-03-19 12:11 hostkey-theta.pem
-rw-r--r-- 1 zsombor zsombor 887 2009-03-19 12:11 hostkey-upsilon.pem

./userCerts:
total 24
-rw-r--r-- 1 zsombor zsombor 778 2009-03-19 12:11 usercert-billy.pem
-rw-r--r-- 1 zsombor zsombor 778 2009-03-19 12:11 usercert-hammer.pem
-rw-r--r-- 1 zsombor zsombor 778 2009-03-19 12:11 usercert-penny.pem
-rw-r--r-- 1 zsombor zsombor 963 2009-03-19 12:11 userkey-billy.pem
-rw-r--r-- 1 zsombor zsombor 963 2009-03-19 12:11 userkey-hammer.pem
-rw-r--r-- 1 zsombor zsombor 951 2009-03-19 12:11 userkey-penny.pem
\end{verbatim}

You can see the certificate and key files for all the hosts and users, and the CA file with the proper hashed name.
There is no rule about where to put these certificate, but it is common to put them in \verb!/etc/grid-security!. Now, create this directory, and a subdirectory called \verb!certificates!. To use the `theta' host certificates for this machine, copy the corresponding certificate and key there:

\begin{verbatim}
$ sudo cp hostCerts/hostcert-theta.pem /etc/grid-security/hostcert.pem
$ sudo cp hostCerts/hostkey-theta.pem /etc/grid-security/hostkey.pem
$ sudo cp CA/* /etc/grid-security/certificates/
$ ls -lR /etc/grid-security/
/etc/grid-security/:
total 12
drwxr-xr-x 2 root root 4096 2009-03-19 12:36 certificates
-rw-r--r-- 1 root root  782 2009-03-19 12:35 hostcert.pem
-rw-r--r-- 1 root root  891 2009-03-19 12:36 hostkey.pem

/etc/grid-security/certificates:
total 8
-rw-r--r-- 1 root root 786 2009-03-19 12:36 66fe707c.0
-rw-r--r-- 1 root root 139 2009-03-19 12:36 66fe707c.signing_policy
\end{verbatim}

@@

\begin{verbatim}
$ mkdir ~/.arc
$ cp userCerts/usercert-billy.pem ~/.arc/usercert.pem
$ openssl rsa -in userCerts/userkey-billy.pem -out ~/.arc/userkey.pem
$ chmod 600 ~/.arc/userkey.pem
$ ls -l ~/.arc
total 8
-rw-r--r-- 1 zsombor zsombor 778 2009-03-19 13:06 usercert.pem
-rw------- 1 zsombor zsombor 891 2009-03-19 13:09 userkey.pem
\end{verbatim}

The storage system runs within the \verb!arched! hosting environment daemon, which needs a configuration file describing which services to be run, on which ports do to listen, etc.
Copy the template configuration files to the \verb!/etc/arc! directory:

\begin{verbatim}
$ sudo mkdir /etc/arc
$ sudo cp arc1/src/services/storage/storage_service.xml.example /etc/arc/storage_service.xml
$ sudo cp arc1/src/services/storage/clientsslconfig.xml /etc/arc
$ ls -l /etc/arc
total 12
-rw-r--r-- 1 root root  259 2009-03-19 13:26 clientsslconfig.xml
-rw-r--r-- 1 root root 4606 2009-03-19 13:25 storage_service.xml
\end{verbatim}

The template configuration file specifies several directories where the services can store their data. Create these directories at, e.g., \verb!/var/spool/arc!.

\begin{verbatim}
$ sudo mkdir /var/spool/arc/ahash_data
$ sudo mkdir /var/spool/arc/shepherd_data
$ sudo mkdir /var/spool/arc/shepherd_store
$ sudo mkdir /var/spool/arc/shepherd_transfer
$ ls -l /var/spool/arc
total 16
drwxr-xr-x 2 root root 4096 2009-03-19 13:42 ahash_data
drwxr-xr-x 2 root root 4096 2009-03-19 13:42 shepherd_data
drwxr-xr-x 2 root root 4096 2009-03-19 13:42 shepherd_store
drwxr-xr-x 2 root root 4096 2009-03-19 13:42 shepherd_transfer
\end{verbatim}

In this deployment the daemon will be run as root, so it is OK that the root owns these directories. 
If creating these directories somewhere else, then modify the paths in the \verb!storage_service.xml! file.

If putting the host certificates and the CA certificate somewhere else than \verb!/etc/grid-security! then modify the \verb!storage_service.xml! (look for \verb!KeyPath!, \verb!CertificatePath! and \verb!CACertificatesDir!). Also, modify \verb!/etc/arc/clientsslconfig.xml!. This file contains the credentials which are used by the services when they connect to an other service. If putting \verb!clientsslconfig.xml! somewhere else than \verb!/etc/arc!, you need to modify all the \verb!ClientSSLConfig! tags in the \verb!storage_service.xml!.

Now, run the \verb!arched! daemon with this config (specified by the \verb!-c! option) first in the foreground (using the \verb!-f! option) to see immediately if everything is right:

@@

The template configuration file specifies a loglevel which only prints error messages, so nothing should be written on the screen now.
The \verb!arched! daemon should now listen on the ports: 60001 for the data transfer service called Hopi, and 60000 for all the other services:

\begin{verbatim}
$ netstat -at | grep LISTEN
tcp        0      0 *:60000                 *:*                     LISTEN     
tcp        0      0 *:60001                 *:*                     LISTEN     
\end{verbatim}

Now it is time to set up the prototype client tool to access the system. It is called \verb!chelonia! and it is by default installed to \verb!/usr/local/bin!. The CLI tool needs to be told where it can find the user credentials, and a URL of a Bartender service. The Bartender service is the front-end of the storage system. This can be specified either by environment variables, or by a configuration file called \verb!~/.arc/client.xml!. Create the following \verb!client.xml! file:

Now you can use the tool \verb!chelonia! to access your local deployment. Try to do a `list' on the root collection (`/'):

\begin{verbatim}
$ chelonia
Usage:
  chelonia <method> [<arguments>]
Supported methods:
  stat - get detailed information about an entry
  makeCollection | make | mkdir - create a collection
  unmakeCollection | unmake | rmdir - remove an empty collection
  list | ls - list the content of a collection
  move | mv - move entries within the namespace
  putFile | put - upload a file
  getFile | get - download a file
  delFile | del | rm - remove a file
  modify | mod - modify metadata
  policy | pol - modify access policy rules
  unlink - remove a link to an entry from a collection without removing the entry itself
  credentialsDelegation | cre - delegate credentials for using gateway
  removeCredentials | rem - remove previously delegated credentials
Without arguments, each method prints its own help.

$ chelonia list
Usage: list <LN> [<LN> ...]

$ chelonia list /
- Calling the Bartender's list method...
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component tcp.client(tcp) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component tls.client(tls) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component http.client(http) could not be created
[2009-03-19 18:37:12] [Arc.Loader] [ERROR] [12491/152991544]
    Component soap.client(soap) could not be created
ERROR: Wrong status from server.
Maybe wrong URL: 'https://localhost:60000/Bartender'
\end{verbatim}

If you get the error `Component [...] could not be created', try to specify to the python environment the location of the python packages:

\begin{verbatim}
$ export PYTHONPATH=/usr/local/lib/python2.5/site-packages/
\end{verbatim}

@@

Now a (centralized) storage service is running, including a Hopi service, which is a basic HTTP server, for transferring files. The Bartender service is the front-end of the system to the users, so the clients always connect to the Bartender service. There are several directories configured in the config file where the services store their data. These directories can always be emptied, which resets the whole system to a clean state. If Chelonia is running with clean data directories, then it is completely empty, meaning that there is not even a root collection:

\begin{verbatim}
$ chelonia list /
- Calling the Bartender's list method...
- done in 0.34 seconds.
'/': not found
\end{verbatim}

@@

\begin{verbatim}
$ chelonia makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.81 seconds.
Creating collection '/': done

$ chelonia list /
- Calling the Bartender's list method...
- done in 0.55 seconds.
'/': collection
    empty.
\end{verbatim}

@@

\section{Using the prototype client tool} % (fold)

Assume that Chelonia is running and you want to access it with the \verb!chelonia! tool. The \verb!~/.arc/client.xml! is set properly, the contents of the root collection can be listed:

\begin{verbatim}
$ chelonia list /
- Calling the Bartender's list method...
- done in 0.55 seconds.
'/': collection
    empty.
\end{verbatim}

@@

\begin{verbatim}
$ cat > orange
orange
$ cat orange 
orange

$ chelonia put orange /
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0003 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 1.26 seconds.
- Got transfer URL: http://localhost:60001/hopi/7fcef91e-ac9c-658d-4def-17d52ba33cfb
- Uploading from 'orange'
    to 'http://localhost:60001/hopi/7fcef91e-ac9c-658d-4def-17d52ba33cfb' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 0.0182 seconds.
'orange' (7 bytes) uploaded as '/orange'.

$ chelonia list /
- Calling the Bartender's list method...
- done in 0.51 seconds.
'/': collection
  orange              <file>

@@

\begin{verbatim}
$ chelonia stat /orange
- Calling the Bartender's stat method...
- done in 0.40 seconds.
'/orange': found
  states
    checksumType: md5
    neededReplicas: 1
    size: 7
    checksum: 6aefd2842be62cd470709b27aedc7db7
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: 12ce831b-eab8-1f47-29f6-19fb85ebf46a
    type: file
  parents
    0/orange: parent
  locations
    https://localhost:60000/Shepherd 3e9ea612-87c0-1e81-58f3-cec6b0b125c1: alive
  timestamps
    created: 1237504821.91
\end{verbatim}

Here, the owner of the file (Billy), the location of the replicas (currently only one), the number of needed replicas (which is also only one), the checksum and size of the file, and the timestamp of the creation is shown.

@@

\begin{verbatim}
$ chelonia get /orange /tmp
- Calling the Bartender's getFile method...
- done in 0.51 seconds.
- Got transfer URL: http://localhost:60001/hopi/521c5869-4c93-8e28-aa3a-03f477f34f63
- Downloading from 'http://localhost:60001/hopi/521c5869-4c93-8e28-aa3a-03f477f34f63'
    to '/tmp/orange' with http...
    0 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0071 seconds.
'/orange' (7 bytes) downloaded as '/tmp/orange'.
$ cat /tmp/orange 
orange
\end{verbatim}

You can create collections which can contain files and other collections forming a tree-hierarchy. You can move files and collection around within this namespace.

\begin{verbatim}
$ chelonia makeCollection /fruits
- Calling the Bartender's makeCollection method...
- done in 0.79 seconds.
Creating collection '/fruits': done

$ chelonia makeCollecion /fruits/apple
- Calling the Bartender's makeCollection method...
- done in 0.91 seconds.
Creating collection '/fruits/apple': done

$ chelonia move /orange /fruits/
- Calling the Bartender's move method...
- done in 0.99 seconds.
Moving '/orange' to '/fruits/': moved

$ chelonia list /fruits
- Calling the Bartender's list method...
- done in 0.60 seconds.
'/fruits': collection
  orange              <file>
  apple               <collection>
\end{verbatim}

You can remove files, and remove collections (but only if the collection is empty):

\begin{verbatim}
$ chelonia rmdir /fruits
- Calling the Bartender's unmakeCollection method...
- done in 0.41 seconds.
Removing collection '/fruits': collection is not empty

$ chelonia rmdir /fruits/apple
- Calling the Bartender's unmakeCollection method...
- done in 0.89 seconds.
Removing collection '/fruits/apple': removed

$ chelonia rm /fruits/orange
- Calling the Bartender's delFile method...
- done in 0.89 seconds.
/fruits/orange: deleted

$ chelonia rmdir /fruits
- Calling the Bartender's unmakeCollection method...
- done in 0.79 seconds.
Removing collection '/fruits': removed
\end{verbatim}

Now, introduce a new user, Penny, into the system. Again, \verb!chelonia! can be told to use user certificate and key files for this user with modifying the \verb!client.xml! or by specifying the \verb!ARC_CERT_FILE! and \verb!ARC_KEY_FILE! environment variables.

\begin{verbatim}
$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
chelonia list /
- Calling the Bartender's list method...
- done in 0.31 seconds.
'/': denied

$ ARC_CERT_FILE=usercert-penny.pem ARC_KEY_FILE=userkey-penny.pem \
chelonia put /tmp/orange /pennys-orange
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0001 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 0.81 seconds.
/pennys-orange: failed to add child to parent

@@

\begin{verbatim}
$ chelonia pol / change ALL +read +addEntry
- Calling the Bartender's stat method...
- done in 0.30 seconds.
old action list for the user ALL was ''
the new action list of user ALL for LN / will be '+read +addEntry'
- Calling the Bartender's modify method...
- done in 0.50 seconds.
set.
\end{verbatim}

@@

\begin{verbatim}
$ chelonia pol
Usage: policy <LN> <changeType> <identity> <action list>
  <changeType> could be 'set', 'change' or 'clear'
    'set': sets the action list to the given user overwriting the old one
    'change': modify the current action list with adding and removing actions
    'clear': clear the action list of the given user
  <identity> could be a '<UserDN>' or a 'VOMS:<VO name>'
  <action list> is a list actions prefixed with '+' or '-'
    e.g. '+read +addEntry -delete'
    possible actions:
        read addEntry removeEntry delete
        modifyPolicy modifyStates modifyMetadata
\end{verbatim}

@@

Now, start the services on \verb!storage2! again, and see what is happening with the file:

>>>>

The Chelonia storage system can be installed from binary packages, or from compiling the source packages. Here we assume that it is installed on every machine we want to use. But we can do a quick check if the ARC client python libraries are installed properly. It is recommended to set the PYTHONPATH variable, e.g.:

\begin{verbatim}
$ export PYTHONPATH=/usr/local/lib/python2.5/site-packages
\end{verbatim}

Then we can check if the packages can be imported:

@@

If there is no error on importing any of the packages, everything is OK.

It is very important to syncronize the time of the machines (at least within a few seconds) - the storage system will make decisions based on differences between timestamps. When deploying multiple machines, different times will cause problems.

In this document we will use a debian lenny system, and we will run multiple versions of the ARC HED hosting environment to simulate multiple machines. We will use three different hostnames , which will in this case point to the same machine, but in real deployment they would of course point to different machines (\verb!chelonia[123].knowarc.eu!).

Host (and user) certificates are required to run the system. For testing purposes the NorduGrid InstantCA solution can be used. The InstantCA is capable of creating a demo-CA with short lifetime. The URL of the InstantCA service is \verb!https://vls.grid.upjs.sk/CA/instantCA!. Now, create 3 user and 3 host certificates. (for this example, we set the Organization Name to `knowarc', the Common name of the CA to `chelonia', the name of the users to `penny', `billy' and `hammer' and the name of the hosts to `chelonia1', `chelonia2' and `chelonia3'. A password for the CA and passwords for the user certificates are needed as well, these should be at least 4 characters long).

@@

\begin{verbatim}
$ ls -lR
.:
total 28
drwxr-xr-x 2 zsombor zsombor 4096 2009-10-16 13:31 CA
-rw-r--r-- 1 zsombor zsombor  951 2009-10-16 13:31 ca.key
-rw-r--r-- 1 zsombor zsombor  778 2009-10-16 13:31 ca.pem
drwxr-xr-x 2 zsombor zsombor 4096 2009-10-16 13:31 hostCerts
-rw-r--r-- 1 zsombor zsombor 1044 2009-10-16 13:31 readme
-rw-r--r-- 1 zsombor zsombor    3 2009-10-16 13:31 serial.srl
drwxr-xr-x 2 zsombor zsombor 4096 2009-10-16 13:31 userCerts

./CA:
total 8
-rw-r--r-- 1 zsombor zsombor 778 2009-10-16 13:31 afc5f10f.0
-rw-r--r-- 1 zsombor zsombor 135 2009-10-16 13:31 afc5f10f.signing_policy

./hostCerts:
total 24
-rw-r--r-- 1 zsombor zsombor 782 2009-10-16 13:31 hostcert-chelonia1.pem
-rw-r--r-- 1 zsombor zsombor 782 2009-10-16 13:31 hostcert-chelonia2.pem
-rw-r--r-- 1 zsombor zsombor 782 2009-10-16 13:31 hostcert-chelonia3.pem
-rw-r--r-- 1 zsombor zsombor 887 2009-10-16 13:31 hostkey-chelonia1.pem
-rw-r--r-- 1 zsombor zsombor 887 2009-10-16 13:31 hostkey-chelonia2.pem
-rw-r--r-- 1 zsombor zsombor 887 2009-10-16 13:31 hostkey-chelonia3.pem

./userCerts:
total 24
-rw-r--r-- 1 zsombor zsombor 769 2009-10-16 13:31 usercert-billy.pem
-rw-r--r-- 1 zsombor zsombor 774 2009-10-16 13:31 usercert-hammer.pem
-rw-r--r-- 1 zsombor zsombor 769 2009-10-16 13:31 usercert-penny.pem
-rw-r--r-- 1 zsombor zsombor 963 2009-10-16 13:31 userkey-billy.pem
-rw-r--r-- 1 zsombor zsombor 963 2009-10-16 13:31 userkey-hammer.pem
-rw-r--r-- 1 zsombor zsombor 963 2009-10-16 13:31 userkey-penny.pem
\end{verbatim}

Here can be seen the certificate and key files for all the hosts and users, and the CA file with the proper hashed name.
There is no rule about where to put these certificate, but it is common to put them in \verb!/etc/grid-security!.

In these examples we assume that the CA certificate is put into \verb!/etc/grid-security/certificates!,

and the host's certificate and key is at \verb!/etc/grid-security/hostcert-chelonia[123].pem!

and \verb!/etc/grid-security/hostkey-chelonia[123].pem!.

\begin{verbatim}
$ ls -l /etc/grid-security/certificates/
total 8
-rw-r--r-- 1 root root 778 2009-10-16 14:55 afc5f10f.0
-rw-r--r-- 1 root root 135 2009-10-16 14:55 afc5f10f.signing_policy
\end{verbatim}

@@

\begin{verbatim}
$ mkdir ~/.arc
$ cp userCerts/usercert-billy.pem ~/.arc
$ openssl rsa -in userCerts/userkey-billy.pem -out ~/.arc/userkey-billy.pem
$ chmod 600 ~/.arc/userkey-billy.pem
$ ls -l ~/.arc
total 8
-rw-r--r-- 1 zsombor zsombor 778 2009-10-16 14:55 usercert-billy.pem
-rw------- 1 zsombor zsombor 891 2009-10-16 14:55 userkey-billy.pem
\end{verbatim}

The storage system runs within the \verb!arched! hosting environment daemon, which needs a configuration file describing which services to be run, on which ports do to listen, etc. There are several profiles for different deployment scenarios, these profiles are installed by default in the \verb!/usr/local/share/arc/profiles! directory\footnote{or they can be acquired from http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/profiles}. First we will use the profile called \verb!CheloniaAllServicesCentralizedAHashWithISIS!. After we have chosen a profile, we need to create a config file which contains the deployment-specific attributes. Let's create a file in \verb!/etc/arc! called \verb!chelonia1.ini!:

\begin{verbatim}
profile=/usr/local/share/arc/profiles/CheloniaAllServicesCentralizedAHashWithISIS.xml

pidfile=/tmp/chelonia1.pid
logfile=/var/log/chelonia1.log
debug=ERROR

port=60001

cacert=/etc/grid-security/certificates
host_cert=/etc/grid-security/hostcert-chelonia1.pem
host_key=/etc/grid-security/hostkey-chelonia1.pem
client_cert=/etc/grid-security/hostcert-chelonia1.pem
client_key=/etc/grid-security/hostkey-chelonia1.pem

[register]
index_server1=https://chelonia1.knowarc.eu:60001/ISIS

[ahash]
endpoint=https://chelonia1.knowarc.eu:60001/AHash
datadir=/var/spool/arc/chelonia1_ahash_data

[bartender]
endpoint=https://chelonia1.knowarc.eu:60001/Bartender

[librarian]
endpoint=https://chelonia1.knowarc.eu:60001/Librarian

[shepherd]
endpoint=https://chelonia1.knowarc.eu:60001/Shepherd
turlprefix=https://chelonia1.knowarc.eu:60001/Hopi
datadir=/var/spool/arc/chelonia1_shepherd_data
storedir=/var/spool/arc/chelonia1_shepherd_store
transferdir=/var/spool/arc/chelonia1_shepherd_transfer

[isis]
endpoint=https://chelonia1.knowarc.eu:60001/ISIS
dbpath=/var/spool/arc/chelonia1_isis_data
peerurl1=https://chelonia1.knowarc.eu:60001/ISIS
\end{verbatim}

In this config we configure several services, and we have some common parts as well. The first line points to the profile which we want to use (please make sure that it is there or specify the correct path). The common parts contains the logfile, the level of debugging, the port to listen, the path to the certificates to be used on the service side, and the certificates to be used when a service wants to connect to an other service (in current case they are the same). Then we have an ISIS service which stores information about the running services and it is needed for the services to find eachother. The register section tells all the other services where to find the ISIS service. And then we have all the storage services: the Bartender, the Librarian, the Shepherd and the A-Hash. The endpoints of the services should be specified for all services. There is one additional service which doesn't need extra configuration: the Hopi service is a lightweight HTTP server. The Shepherd service is connected to the Hopi service, that's why it is needed to specify the Hopi's URL in the Shepherd's section (\verb!turlprefix!). Some of these services need to have directories to store data. We will use subdirectories in \verb!/var/spool/arc!, so we have to create this directory first:

\begin{verbatim}
$ sudo mkdir /var/spool/arc
\end{verbatim}

Now, run the \verb!arched! daemon with this INI config which is specified with the \verb!-i! option. (In this document we will run the ARC HED daemon as root.) We can first run it in the foreground (with the \verb!-f! flag), to see the possible initial misconfiguration errors immediately:

@@

When we start the services, they are trying hard to find eachother, which means lots of connection related error messages in the beginning, but after a minute or so, the system should stabilize. (This is the case with shutdown as well, it is normal to get lots of connection related error messages). The \verb!arched! daemon should now listen no port 60001:

\begin{verbatim}
$ netstat -at | grep 60001
tcp        0      0 *:60001                 *:*                     LISTEN     
\end{verbatim}

Now it is time to set up the client tool to access the system. It is called \verb!chelonia! and it is by default installed to \verb!/usr/local/bin!. The CLI tool needs to be told where it can find the user credentials, and a URL of one or more Bartender services or preferably the URL of one or more ISIS services, where Bartender services are registered. The Bartender service is the front-end of the storage system. These can be specified with a config file, which is called \verb!~/.arc/client.conf! by default:

\begin{verbatim}
defaultservices=index:ARC1:https://chelonia1.knowarc.eu:60001/ISIS
keypath=/home/zsombor/.arc/userkey-billy.pem
certificatepath=/home/zsombor/.arc/usercert-billy.pem
cacertificatesdirectory=/etc/grid-security/certificates
\end{verbatim}

Now we can use the tool \verb!chelonia! to access the local deployment. If our client.conf is not at the default directory, then we can specify the path with the \verb!-z! flag. First let's try to do a `list' on the root collection (`/'):

\begin{verbatim}
zsombor@chelonia:~$ chelonia list /
ERROR: No Bartender URL found.
(use the '-v' flag for more details, e.g. 'chelonia -v list /')
\end{verbatim}

If we get this error message, we should call it again with the \verb!-v! verbose flag:
\begin{verbatim}
zsombor@chelonia:~$ chelonia -v list /
- Using default user config.
- The key file: /home/zsombor/.arc/userkey-billy.pem
- The cert file: /home/zsombor/.arc/usercert-billy.pem
- The CA dir: /etc/grid-security/certificates
- No Bartender URL found in the config or in the environment, try to get one from ISIS:
[2009-10-20 14:11:34] [Arc.Loader] [ERROR] [19139/149632560]
    Component tcp.client(tcp) could not be created
[2009-10-20 14:11:34] [Arc.Loader] [ERROR] [19139/149632560]
    Component tls.client(tls) could not be created
[2009-10-20 14:11:34] [Arc.Loader] [ERROR] [19139/149632560] 
    Component http.client(http) could not be created
[2009-10-20 14:11:34] [Arc.Loader] [ERROR] [19139/149632560] 
    Component soap.client(soap) could not be created
  - https://chelonia1.knowarc.eu:60001/ISIS - Failed to connect to ISIS.
ERROR: No Bartender URL found.
\end{verbatim}

If we get the error `Component [...] could not be created', it is usually because python somehow doesn't find the ARC clien libraries, so let's check if we have the PYTHONPATH  variable set properly, and set it, if not:

\begin{verbatim}
$ echo $PYTHONPATH

$ export PYTHONPATH=/usr/local/lib/python2.5/site-packages/
\end{verbatim}

@@

Now a (centralized) Chelonia is running, including a Hopi service, which is a basic HTTP server, for transferring files. The Bartender service is the front-end of the system to the users, so the clients always connect to the Bartender service. There are several directories configured in the config file where the services store their data. These directories can always be emptied, which resets the whole system to a clean state. If Chelonia is running with clean data directories, then it is completely empty, meaning that there is not even a root collection:

\begin{verbatim}
$ chelonia list /
'/': not found
\end{verbatim}

@@

\begin{verbatim}
$ chelonia mkdir /
Creating collection '/': done

$ chelonia list /
'/': collection
    empty.
\end{verbatim}

@@

\section{Using the chelonia client tool} % (fold)

We assume that Chelonia is running and can be accessed with the \verb!chelonia! tool. The \verb!~/.arc/client.conf! is set properly, the contents of the root collection can be listed:

\begin{verbatim}
$ chelonia list /
'/': collection
    empty.
\end{verbatim}

@@

\begin{verbatim}
$ echo ORANGE > orange
$ cat orange 
ORANGE

$ chelonia put orange /
'orange' (7 bytes) uploaded as '/orange'.

$ chelonia list /
'/': collection
  orange <file>
\end{verbatim}

@@

\begin{verbatim}
$ chelonia stat /orange
'/orange': found
  states
    checksumType: md5
    neededReplicas: 3
    size: 7
    checksum: a7992bd22ce079983da12c0172983ff4
  entry
    owner: /DC=eu/DC=KnowARC/O=knowarc/CN=billy
    GUID: eb973cb4-7924-0663-2b3e-13c01203fcd1
    type: file
  parents
    0/orange: parent
  locations
    https://chelonia1.knowarc.eu:60001/Shepherd 630b9bf0-7b70-8e04-1098-01769af3f8ea: alive
  timestamps
    created: 1256041232.28
\end{verbatim}

Here, the owner of the file (Billy), the location of the replicas (currently only one), the number of needed replicas (which is three), the checksum and size of the file, and the timestamp of the creation is shown.

@@

\begin{verbatim}
$ chelonia get /orange /tmp
'/orange' (7 bytes) downloaded as '/tmp/orange'.

$ cat /tmp/orange 
ORANGE
\end{verbatim}

We can create collections which can contain files and other collections forming a tree-hierarchy. We can move files and collection around within this namespace.

\begin{verbatim}
$ chelonia mkdir /fruits
Creating collection '/fruits': done

$ chelonia mkdir /fruits/apple
Creating collection '/fruits/apple': done

$ chelonia mv /orange /fruits
Moving '/orange' to '/fruits': targetexists
\end{verbatim}

Note that if we want to move something into a colleciton, we have to end the collection's logical name with a slash:

\begin{verbatim}
$ chelonia mv /orange /fruits/
Moving '/orange' to '/fruits/': moved

$ chelonia ls /fruits
'/fruits': collection
  orange <file>
  apple  <collection>
\end{verbatim}

We can remove files, and remove collections (but only if the collection is empty):

\begin{verbatim}
$ chelonia rmdir /fruits
Removing collection '/fruits': collection is not empty

$ chelonia rmdir /fruits/apple
Removing collection '/fruits/apple': removed

$ chelonia rm /fruits/orange
/fruits/orange: deleted

$ chelonia rmdir /fruits
Removing collection '/fruits': removed
\end{verbatim}

Now, let's introduce a new user, Penny, into the system. The easiest would be to create a new client.conf for Penny:

\begin{verbatim}
$ cat /home/zsombor/.arc/penny.conf 
defaultservices=index:ARC1:https://chelonia1.knowarc.eu:60001/ISIS
keypath=/home/zsombor/.arc/userkey-penny.pem
certificatepath=/home/zsombor/.arc/usercert-penny.pem
cacertificatesdirectory=/etc/grid-security/certificates    
\end{verbatim}

We should copy her certificate and key the same way as we did with Billy's certificate and key. Then we can specify Penny's config with the \verb!-z! flag (and we can use the \verb!-v! flag to see what is happening:

\begin{verbatim}
$ chelonia -v -z ~/.arc/penny.conf list /
- Config file specified: /home/zsombor/.arc/penny.conf
- The key file: /home/zsombor/.arc/userkey-penny.pem
- The cert file: /home/zsombor/.arc/usercert-penny.pem
- The CA dir: /etc/grid-security/certificates
- No Bartender URL found in the config or in the environment, try to get one from ISIS:
  - https://chelonia1.knowarc.eu:60001/ISIS - Got Bartender URL from ISIS: https://chelonia1.knowarc.eu:60001/Bartender
- The URL of the Bartender(s): https://chelonia1.knowarc.eu:60001/Bartender
- Calling the Bartender's list method...
- Trying https://chelonia1.knowarc.eu:60001/Bartender...
- done in 0.15 seconds.
'/': denied

$ chelonia -z ~/.arc/penny.conf put orange /pennys-orange
/pennysorange: failed to add child to parent
\end{verbatim}

@@

\begin{verbatim}
$ chelonia policy / change ALL +read +addEntry
Setting action list of '/' for user ALL to +read +addEntry: set.
\end{verbatim}

@@

\begin{verbatim}
$ chelonia pol
$ chelonia policy
Usage: policy <LN> <changeType> <identity> <action list>
  <changeType> could be 'set', 'change' or 'clear'
    'set': sets the action list to the given user overwriting the old one
    'change': modify the current action list with adding and removing actions
    'clear': clear the action list of the given user
  <identity> could be a '<UserDN>' or a 'VOMS:<VO name>'
  <action list> is a list actions prefixed with '+' or '-'
    e.g. '+read +addEntry -delete'
    possible actions:  read addEntry removeEntry delete
                       modifyPolicy modifyStates modifyMetadata
\end{verbatim}

@@

Let's start \verb!chelonia2! again, and check the state of the replicas:
